Relationship Between Stock Prices and Common Financial Metrics

### 2024-04-02 outputs/paper/paper.qmd
title
link

---
title: "Relationship Between Stock Prices and Common Financial Metrics"
subtitle: "Analysis of the Relationship Between Stock Price and EPS & Dividends of the Largest 50 North American Companies over 10 Years"
author: Diana Liu
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

@@

saveRDS(
  model_1,
  file = "model_1.rds"
)
```

@@

saveRDS(
  model_rstanarm_2,
  file = "model_rstanarm_2.rds"
)
```

>>>>

---
title: "Relationship Between Stock Prices and Common Financial Metrics"
subtitle: "Analysis of the Relationship Between Stock Price and EPS & Dividends of the Largest 50 North American Companies over 10 Years"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Relationship-Between-Stock-Prices-and-Common-Financial-Metrics"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@@

saveRDS(
  model_1,
  file = "~/Stock-Prices/outputs/models/model_1.rds"
)
```

@@

saveRDS(
  model_rstanarm_2,
  file = "~/Stock-Prices/outputs/models/model_rstanarm_2.rds"
)
```
